pirouette: Determining the error BEAST2 makes in inferring a phylogeny

### 2019-03-13 article.tex
Improve introduction

However, in many cases the computation of this likelihood (the tree prior) 
is computationally demanding and it is unfeasible to use it 
in a Bayesian inference framework where it needs to be 
computed millions to billions of times.
However, if the data are very informative, the influence of the prior 
is often relatively small, and hence under this assumption 
it has become common practice to use already existing BEAST2 priors. 
However, it is unclear whether this assumption holds.
Here we introduce a pipeline to assess this assumption 
for any given diversification model. 
Briefly, it consists of the following steps: 
first simulate a phylogeny 
according to the mechanisms proposed by the new diversification model, 
then simulate a nucleotide alignment 
and use current inference tools (such as BEAST2) to estimate the phylogeny. 
If the estimated tree differs only slightly from the original phylogeny, 
the original assumption is justified and the simple diversification models 
in the inference tools suffice. 
If the trees differ markedly, it will be worth the effort and computational burden 
to develop a species tree module to be used in these tools.
Our pipeline is programmed as an R package and is called 
\verb;pirouette; it is built on \verb;babette; [Bilderbeek \& Etienne, 2018], 
which calls BEAST2 [\cite{bouckaert2014beast}]. 
With \verb;pirouette;, one
can easily measure the error made by Bayesian inference in recovering
any given phylogeny, helping us to evaluate the necessity of a new diversification model.

>>>>

Not all diversification models that pass the procedure described above
are used in Bayesian inference.
In Bayesian inference, the likelihood of a diversification 
model, also called tree prior, is computed millions of time.
Due to this, effective but computationally expensive tree priors 
are unused in Bayesian inference.
Also, there may be no need to add such a tree prior to a Bayesian
inference framework: the more informative the data, 
the lower the influence of the tree prior.
Due to this, existing and easy to compute tree priors are most commonly used.
However, it is unknown if it is valid to assume that tree prior choice is 
of low importance.
Here we introduce a pipeline to assess this assumption and quantify the
effect of the tree prior of any given diversification model. 
Briefly, it consists of the following steps: 
first simulate a phylogeny 
according to the mechanisms proposed by the new diversification model, 
then simulate a nucleotide alignment 
and use current inference tools (such as BEAST2) to estimate the phylogeny. 
If the estimated tree differs only slightly from the original phylogeny, 
the original assumption is justified and the simple diversification models 
in the inference tools suffice. 
If the trees differ markedly, it will be worth the effort and computational burden 
to develop a species tree module to be used in these tools.
Our pipeline is programmed as an R package and is called 
\verb;pirouette; it is built on \verb;babette; [Bilderbeek \& Etienne, 2018], 
which calls BEAST2 [\cite{bouckaert2014beast}]. 
With \verb;pirouette;, one
can easily measure the error made by Bayesian inference in recovering
any given phylogeny, helping us to evaluate the necessity of a new diversification model.
